  ---
title: "Data analysis"
author: "Jae Yeon Kim"
output:
html_document: 
  toc: true
  theme: united
---


## 0. Setup 

I tweaked the global option of the R Markdown to enlarge figures produced by ggplot2.

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8, 
                      echo = FALSE, warning = FALSE, message = FALSE) # global setting for enlarging image size
```

```{r}

# Clean up the environment

rm(list = ls())

# Import libraries (adapted from this link: https://stackoverflow.com/questions/4090169/elegant-way-to-check-for-missing-packages-and-install-them)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
        tidyverse, # for the tidyverse framework
        ggpubr, # for arranging ggplots   
        ggthemes, # for fancy ggplot themes
        estimatr, # for fast estimation for design-based inference
        DACF, # for ceiling and or/floor data 
        MKinfer, # for inferential statistics
        nonpar # for nonparametric inference
)


source("/home/jae/analyzing-list-experiments/functions/theme_publications.r")

theme_set(theme_Publication(14))
```

## 1. Importing data

```{r}

# The processed data 
df <- read.csv("/home/jae/analyzing-list-experiments/processed_data/processed_survey.csv")

```
  
## 2. Testing ceiling and/or floor effect 

```{r}

df %>%
  gather(measures, responses, c(direct, indirect)) %>%
  ggplot(aes(x = responses)) +
    geom_density() +
    facet_grid(measures~treat) +    
    labs(x = "Responses", y = "Density")

```

## 3. Average treatment effect (ATE)

- By random assignment, difference-in-means is an unbiased estimator of the average treatment effect.
- Still, there's a concern about sampling variability. I address that by conducting t-tests. Here, the null hypothesis the average treatment effect is 0.

### 3.1. Creating a function 

```{r}

diff_means_test <- function(data) {
  
  diff_summary <- data %>%

    # Summarize 
    summarise_each(
      funs(
        
        # Different in means 
        diff_t1 = mean(.[treat == 2], na.rm = T) - mean(.[treat == 1], na.rm = T),
        diff_t2 = mean(.[treat == 3], na.rm = T) - mean(.[treat == 1], na.rm = T),
        diff_t3 = mean(.[treat == 4], na.rm = T) - mean(.[treat == 1], na.rm = T),
        diff_t4 = mean(.[treat == 5], na.rm = T) - mean(.[treat == 1], na.rm = T),

        # Calculating confidence intervals
        conf_t1 = (t.test(.[treat == 2], .[treat == 1])$conf.int[2] - t.test(.[treat == 1], .[treat == 1])$conf.int[1]) / 2,
        conf_t2 = (t.test(.[treat == 3], .[treat == 1])$conf.int[2] - t.test(.[treat == 1], .[treat == 1])$conf.int[1]) / 2,
        conf_t3 = (t.test(.[treat == 4], .[treat == 1])$conf.int[2] - t.test(.[treat == 1], .[treat == 1])$conf.int[1]) / 2,
        conf_t4 = (t.test(.[treat == 5], .[treat == 1])$conf.int[2] - t.test(.[treat == 1], .[treat == 1])$conf.int[1]) / 2
      ),
      direct, indirect
    )
  
  diff_summary %>%
    gather(stat, val) %>% # stat = variables, val = values 
    separate(stat, into = c("var", "stat", "treat"), sep = "_") %>% # var = measures, stat = diff or conf, group = treatment status, val = values  
    spread(stat, val) %>% # reorder columns
    mutate(var = replace(var, var == "direct", "Direct bias")) %>% # rename variables 
    mutate(var = replace(var, var == "indirect", "Indirect bias")) 

}

```

### 3.2. ATE outcomes

```{r}

# Save test results
ate.results <- diff_means_test(df) 

# Recode values 
ate.results$treat <- ate.results$treat %>%
  recode(t1 = "Low-income S. Koreans",
         t2 = "North Korean refugees",
         t3 = "Korean Chinese migrants",
         t4 = "Indonesian migrants")

# Tidy model ouutcomes 
ate.results

```

## 4. Conditional ATE

### 4.1. Subsetting

```{r}

conservatives <- df %>% filter(ideology <= 2)

moderates <- df %>% filter(ideology == 3)

liberals <- df %>% filter(ideology == 4 | ideology == 5)

undecided <- df %>% filter(ideology == 6)

```

### 4.2. Conditional ATE outcomes

```{r}

cate.results <- bind_rows(
mutate(diff_means_test(conservatives), subgroup = "Conservatives"),
mutate(diff_means_test(moderates), subgroup = "Moderates"),
mutate(diff_means_test(liberals), subgroup = "Liberals"),
mutate(diff_means_test(undecided), subgroup = "Undecided")
)

# Recode values 
cate.results$treat <- cate.results$treat %>%
  recode(t1 = "Low-income S. Koreans",
         t2 = "North Korean refugees",
         t3 = "Korean Chinese migrants",
         t4 = "Indonesian migrants")

# Tidy model ouutcomes 
cate.results

```

## 5. Bootstrapping  

### 5.1. Using boot.t.test

```{r}
boot_dmt <- function(data) {
  
  diff_summary <- data %>%

    # Summarize 
    summarise_each(
      funs(
        
        # Different in means 
        diff_t1 = mean(.[treat == 2], na.rm = T) - mean(.[treat == 1], na.rm = T),
        diff_t2 = mean(.[treat == 3], na.rm = T) - mean(.[treat == 1], na.rm = T),
        diff_t3 = mean(.[treat == 4], na.rm = T) - mean(.[treat == 1], na.rm = T),
        diff_t4 = mean(.[treat == 5], na.rm = T) - mean(.[treat == 1], na.rm = T),

        # Calculating confidence intervals
        conf_t1 = (MKinfer::boot.t.test(.[treat == 2], .[treat == 1], R = 1000)$boot.conf.int[2] - MKinfer::boot.t.test(.[treat == 1], .[treat == 1], R = 1000)$boot.conf.int[1]) / 2,
        conf_t2 = (MKinfer::boot.t.test(.[treat == 3], .[treat == 1], R = 1000)$boot.conf.int[2] - MKinfer::boot.t.test(.[treat == 1], .[treat == 1], R = 1000)$boot.conf.int[1]) / 2,
        conf_t3 = (MKinfer::boot.t.test(.[treat == 4], .[treat == 1], R = 1000)$boot.conf.int[2] - MKinfer::boot.t.test(.[treat == 1], .[treat == 1], R = 1000)$boot.conf.int[1]) / 2,
        conf_t4 = (MKinfer::boot.t.test(.[treat == 5], .[treat == 1], R = 1000)$boot.conf.int[2] - MKinfer::boot.t.test(.[treat == 1], .[treat == 1], R = 1000)$boot.conf.int[1]) / 2
      ),
      direct, indirect
    )
  
  diff_summary %>%
    gather(stat, val) %>% # stat = variables, val = values 
    separate(stat, into = c("var", "stat", "treat"), sep = "_") %>% # var = measures, stat = diff or conf, group = treatment status, val = values  
    spread(stat, val) %>% # reorder columns
    mutate(var = replace(var, var == "direct", "Direct bias")) %>% # rename variables 
    mutate(var = replace(var, var == "indirect", "Indirect bias")) 

}


```

### 5.2. Recalculating CIs for CATE

```{r}

boot.cate.results <- bind_rows(
mutate(boot_dmt(conservatives), subgroup = "Conservatives"),
mutate(boot_dmt(moderates), subgroup = "Moderates"),
mutate(boot_dmt(liberals), subgroup = "Liberals"),
mutate(boot_dmt(undecided), subgroup = "Undecided")
)

# Recode values 
boot.cate.results$treat <- boot.cate.results$treat %>%
  recode(t1 = "Low-income S. Koreans",
         t2 = "North Korean refugees",
         t3 = "Korean Chinese migrants",
         t4 = "Indonesian migrants")

# Tidy model ouutcomes 
boot.cate.results

```

## 6. Visualizing results 

```{r}

ate.results %>%
  ggplot(aes(x = fct_reorder(treat, diff), y = diff, ymin = diff - conf, ymax = diff + conf, col = var)) +
  geom_pointrange() +
  geom_hline(yintercept = c(0), linetype = "dotted") +
  coord_flip() + 
  scale_colour_manual(values = c("Direct bias" = "red", "Indirect bias" = "blue")) +
  labs(title = "Treatment effects",
  subtitle = " Direct bias: X group is stupid. \n Indirect bias: X group doesn't deserve support.",
  caption = "Source: Original mobile survey (N = 1464)",
  x = "Treatment status", y = "Estimated Average Treatment Effect",
  col = "Bias type") 

ggsave("/home/jae/analyzing-list-experiments/outputs/ate_results_plot.png", width = 10)

no_boot_plot <- cate.results %>%
  ggplot(aes(x = fct_reorder(subgroup, diff), y = diff, ymin = diff - conf, ymax = diff + conf, col = var)) +
  geom_pointrange() +
  geom_hline(yintercept = c(0), linetype = "dotted") +
  coord_flip() +
  scale_colour_manual(values = c("Direct bias" = "red", "Indirect bias" = "blue")) +
  facet_wrap(~treat) +
  labs(title = "Heterogeneous treatment effects",
  subtitle = "Direct bias: X group is stupid. Indirect bias: X group doesn't deserve support.",
  caption = "Source: Original mobile survey (N = 1464)",
  x = "Conditions", y = "Conditional Estimated Average Treatment Effect",
  col = "Bias type") +
  ylim(c(-0.4, 1.2))

boot_plot <- boot.cate.results %>%
  ggplot(aes(x = fct_reorder(subgroup, diff), y = diff, ymin = diff - conf, ymax = diff + conf, col = var)) +
  geom_pointrange() +
  geom_hline(yintercept = c(0), linetype = "dotted") +
  coord_flip() +
  scale_colour_manual(values = c("Direct bias" = "red", "Indirect bias" = "blue")) +
  facet_wrap(~treat) +
  labs(title = "Heterogeneous treatment effects (with Bootstrapped CIs)",
  subtitle = "Direct bias: X group is stupid. Indirect bias: X group doesn't deserve support.",
  caption = "Source: Original mobile survey (N = 1464)",
  x = "Conditions", y = "Conditional Estimated Average Treatment Effect",
  col = "Bias type") +
  ylim(c(-0.4, 1.2))

ggarrange(no_boot_plot, boot_plot, common.legend = TRUE,
          ncol = 1, nrow = 2)

ggsave("/home/jae/analyzing-list-experiments/outputs/cate_comparison_plot.png", width = 10, height = 10)
```